I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-15 Paper/introduction.tex

For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities). On simple networks, such as those trained robust, 
this is particularly efficient because branch and bound can find very efficiently the bounds
focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider and not enough can be discarded early.

On such complex DNN, $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are computed using the (exact) MILP encoding, with a time-out, reporting the best bounds that can be obtained. In our algorithm, this is pushed to all layers, which is possible in our case as we select only a limited number of important ReLU nodes to encode as binary variables, while this would be infeasible without the selection based on the compensating pairs. The refined version is particularly efficient on small networks, but as the network grows, the more work BaB needs to do and faces the same wall, and our algorithm becomes more accurate.

@@

Finally, algoirthms resorting to absraction on the network (e.g. Reluplex/Marabou \cite{Reluplex,Marabou}) rather than abstraction on the values are much more different. These algorithms have been developped to be complete, so much slower but also more accurate than what we propose.

>>>>

@@

For comparison, $\alpha$-$\beta$ CROWN \cite{crown} (and other Branch and Bound algorithms, such as \cite{BaB}) will run few instances of branch and bound (one per output neuron), in worst case considering all the possible ReLU configurations (although the branch and bound algorithm avoids most of the possibilities). On simple networks, such as those trained robust, this is particularly efficient because branch and bound can find very efficiently the bounds focusing on the actual question, considering the important branchs, while our algorithm will be less efficient as it has to consider each nodes one by one from the start.
However, branch and bound faces a complexity wall when the network is hard to verify, such as the DNNs trained naturally, as there are too many branches to consider.

On such complex DNN, PRIMA and $\alpha$-$\beta$ CROWN resorts to a "refined" path, where the bounds on the first few layers are refined using MILP on the exact encoding \cite{MILP2}. In our algorithm, we do not use an exact encoding but a partial one with the most important
ReLU nodes obtained by considering the compensation strength. As it is much more efficient, 
this can be pushed to all layers, while this would be infeasible without the selection based on the compensation. The refined version of $\alpha$-$\beta$ CROWN is particularly efficient on small  DNNs, but as the depth grows, the more work BaB needs to do and our algorithm 
is more accurate, lowering the gap of verified images to the upper bound down from $17.6\%$ to $12\%$.

Finally, algorithms resorting to absraction on the network (e.g. Reluplex/ Marabou \cite{Reluplex,katz2019marabou}) rather than abstraction on the values are much more different. These algorithms have been developped to be complete, so much slower but also more accurate than what we propose.
